Deep learning for geophysics

### 2023-10-10 manuscript.tex
Spell check and adjust chapter structure
Make compilable
Cleverref and subfiles seem to interact poorly, and I can't cref labels in external files in the way I had set up.

I've moved to using  \include.
Update titlepage

\documentclass[12pt,a4paper]{report} %,openright,twoside
\usepackage{thesisstyle}
\addbibresource{bib/PhD.bib}
\begin{document}

\begin{titlepage}

    \begin{center}
        \large{\textbf{Potential Field Geophysics Enhancement Using Contemporary Deep Learning Approaches}}

        \vspace{15 mm}
        {\large{Luke Thomas Smith, BSc, MRes}}

        \vspace{15 mm}
        This thesis is presented for the degree of

        \vspace{5 mm}
        \textbf{Doctor of Philosophy}

@@

        \textbf{The University of Western Australia}
        \vspace{5 mm}

        School of Earth Sciences
        \vspace{20 mm}

        \begin{figure}[h]
            \centering{}
            \includegraphics[scale=0.5]{fig/etc/UWA_FORMAL_PORTRAIT_CMYK}
        \end{figure}

        \vspace*{\fill}
        2023
    \end{center}
\end{titlepage}

@@

\newpage{}
\tableofcontents{}
\listoffigures{}
\listoftables{}

@@

\chapter{Introduction}
\label{ch:intro}
\subfile{intro}

\chapter{Magnetic Grid Resolution Enhancement using Machine Learning}
\label{ch:paper1}
This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.

Smith, L., Horrocks, T., Holden, E.-J., Wedge, D., Akhtar, N., 2022. Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane. Ore Geology Reviews 150, 105119.
https://doi.org/10.1016/j.oregeorev.2022.105119
\subfile{paper1}

\chapter{Super-resolution of Aeromagnetic Survey Data}
\label{ch:paper2}
\subfile{paper2}

\chapter{Implicit Neural Representation for Potential Field Geophysics}
\label{ch:paper3}
% \subfile{paper3}

\chapter{Discussion}
\label{ch:discussion}
\subfile{discussion}

>>>>

\documentclass[12pt,a4paper]{report} %,openright,twoside
% \includeonly{}
\usepackage{thesisstyle}
\addbibresource{bib/PhD.bib}
\begin{document}

\begin{titlepage}
    \centering

        \vspace*{48 pt}
        {\large\textbf{Potential Field Geophysics Enhancement Using Contemporary Deep Learning Approaches}}

        \vspace{48 pt}
        {\itshape{{\Large Luke Thomas Smith}, BSc, MRes}}

        \vspace{48 pt}
        This thesis is presented for the degree of

        \vspace{14 pt}
        \textbf{Doctor of Philosophy}

@@

        \textbf{The University of Western Australia}

        \vspace{14 pt}
        School of Earth Sciences

        \vspace{72 pt}
        \includegraphics[scale=0.35]{fig/etc/UWA_FORMAL_PORTRAIT_CMYK}

        \vspace*{\fill}
        2023
\end{titlepage}

@@

\newpage{}
\tableofcontents{}
\listoffigures{}
% \listoftables{}

@@

\chapter{Introduction}
% \subfile{intro}
% \includepdf[pages=-]{intro.pdf}
\include{intro}

\chapter{Magnetic Grid Resolution Enhancement using Machine Learning}
\label{paper1}
This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.

Smith, L., Horrocks, T., Holden, E.-J., Wedge, D., Akhtar, N., 2022. Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane. Ore Geology Reviews 150, 105119.
https://doi.org/10.1016/j.oregeorev.2022.105119
% \subfile{paper1}
% \includepdf[pages=-]{paper1.pdf}
\include{paper1}

\chapter{Super-resolution of Aeromagnetic Survey Data}
\label{paper2}
% \includepdf[pages=-]{paper2.pdf}
% \subfile{paper2}
\include{paper2}

\chapter{Implicit Neural Representation for Potential Field Geophysics}
\label{paper3}
% \includepdf[pages=-]{paper3.pdf}
% \subfile{paper3}
\include{paper3}

% \includepdf[pages=-]{discussion.pdf}
% \subfile{discussion}
\include{discussion}
